The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2019-09-09 tex/VHzQ.tex
Updated the Appendix, modifying Table C2 and text

We initially downloaded the 20190514 version of the Perger
catalogue\footnote{http://astro.elte.hu/~perger/catalog.html} again
matching on a $2\arcsec$ radius.  We found 10 objects (see
Table~\ref{tab:disagree_objs}) that were in both catalogues but had
disagreement on the coordinates.  Two particular odd examples were
SDSSJ0835+3227 and VA-13492.  In both cases the coordinates looked
similar to SDSSJ0835+3217 and SDSSJ1040-1155, respectively, and the
redshifts were identical to these quasars.

In the case of SDSSJ0835+3227, we checked the SDSS $z$-band
images\footnote{https://dr15.sdss.org}, and found a bright source at
the position of SDSSJ0835+3217 and no source at the position of
SDSSJ0835+3227, see Figure~\ref{fig:check_obj}. In the case of
VA-13492, the $i$-band magnitude was equivalent to SDSS J1040-1155
($i=25.9$ mag), so we have decided that both of these objects have
been transcribed incorrectly sometime in the past.

The objects from the submitted version of Ross \& Cross that have
changed position are flagged in Table~\ref{tab:disagree_objs}. The
Perger catalogue has been updated to the 20190724 version (which
matches our catalogue). A final test of matching to with $1\arcsec$
found another difference: we had downloaded the OGLEJ015531-75
coordinates from the published paper and Perger had done so from the
submitted arXiv paper - and \cite{Kozlowski2019} made a minor update
to the positional values in between.

We exclude DES0141-54 that is in the Perger catalogue from our final
sample. This object came from a conference proceedings
\cite{Belladitta2018}, which did not have arcsecond precision in its
coordinates so we could not perform our matched-aperture photometry.

Our final catalogue has 488 $z\geq$ QSOs, see Table~\ref{tab:new_qsos}.}

@@

\iffalse
\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
QSO & ra & dec & difference & isCRDiff & Issue \\
 & deg & deg & arcsec & &  \\
\hline
OGLEJ015531-752807 & +28.8792083 & -75.4686111 & 1.1 & No & 1 \\
%% Same name diff pos/redshift from v1
PSOJ009.7355-10.4316 & +9.7355079 & -10.4316386	& 0. & Yes & 3 \\
ATLASJ025.6821-33.4627 & +25.6821972 & -33.4626300 & 0. & Yes & 3 \\ 
SDWISEJ0155+0415 & +28.8886666 & +4.2518725	& 0. & Yes & 3 \\
PSOJ065.4085-26.9543 & +65.4085370 & -26.9543351 & 0. & Yes & 3 \\ 
VDESJ0454-4448 & +73.5074500 & -44.8086400 & 0.	& Yes & 3 \\ 
DELSJ1048-0109 & +162.0795417 & -1.1611694 & +12.1 & Yes & 2,3,4 \\
SDSSJ1306+0356 & +196.5344701 & +3.9406556 & 0.	& Yes & 3 \\
PSOJ217.0891-16.0453 & +217.0891328	& -16.0453608 & 0. & Yes & 3 \\
SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & +150.0 & Yes & 2 \\
DELSJ1559+2212 & +239.7878750 & +22.2040083	& +3.0 & Yes & 2 \\ 
ATLASJ332.8017-32.1036 & +332.8017500 &	-32.1035556	& +3.2 & Yes & 2,3 \\
PSOJ340.2041-18.6621 & +340.2041700	& -18.6621700 & 0. & Yes & 3 \\ 
VIKJ2318-3113 & +349.5764625 &-31.2295417 & 239.9 & Yes & 2,3 \\
PSOJ359.1352-06.3831 & +359.1352149	& -6.3831264 & 0. & Yes & 3 \\
%%Krisztina wrong\ldots
SDSSJ1621+5155 & +245.2538300 & +51.9302200	& 0. & No & 5 \\
DELSJ1135+5011 & +173.7872080 & +50.1924999	& 0. & No & 5 \\
DELSJ0839+3900 & +129.9453330 & +39.0031944	& 0. & No & 5 \\
%% More complex 
SDSSJ0835+3227 & --- & --- & --- & No & 6 \\
VA-13492 & --- & --- & --- & No & 6 \\
\hline  \hline
\end{tabular}
\caption{{\bf QSOs in disagreement between RC and Perger or which have been
updated since the submitted paper.
This table shows all of the QSOs where there has been a disagreement or a
change. All of those marked 'Yes' were in the submitted paper and have been
changed since, and the final column lists the reason(s) for inclusion in the
table. The numbers refer to the following issues:
1) Coordinate update in original reference, from submitted to accepted; 
2) Coordinate different in RC submitted;
3) Redshift different in RC submitted, typically very small changes;
4) Our coords incorrect, but KP had 2 entries, one also incorrect;
5) Coordinates incorrect in KP;
6) Two objects with similar looking coordinates and identical redshifts. These
appear to be incorrect entries further back in the literature;}
}
\label{tab:disagree_objs}
\end{table*}
\fi

>>>>

We initially downloaded the 20190514 version of the Perger
catalogue\footnote{http://astro.elte.hu/$\sim$perger/catalog.html} again
matching on a $2\arcsec$ radius. We found several objects that were in both
catalogues but had disagreement on the coordinates. Most of these were
fixed by checking the literature for the original catalogue.

There were two QSOs in the Perger catalogue which could not be immediately fixed
by looking up the original coordinates in the literature: SDSSJ0835+3227 and VA-13492.
In both cases the coordinates looked similar to SDSSJ0835+3217 and
SDSSJ1040-1155, respectively, and the stated redshifts were identical to these
quasars. In the case of SDSSJ0835+3227, we checked the SDSS $z$-band
images\footnote{https://dr15.sdss.org}, and found a bright source at
the position of SDSSJ0835+3217 and no source at the position of
SDSSJ0835+3227, see Figure~\ref{fig:check_obj}. In the case of
VA-13492, the $i$-band magnitude was equivalent to SDSS J1040-1155
($i=25.9$ mag), so we have decided that both of these objects have
been transcribed incorrectly sometime in the past. The SDSSJ1040-1155 
transcription error seems to have occurred after \cite{Douglas2007} and is in
\cite{Flesch2015}, so it probably occurred in the \cite{Flesch2015}.

The five objects from the submitted version of Ross \& Cross that have
changed position are in Table~\ref{tab:disagree_objs}. The
Perger catalogue has been updated to the 20190724 version (which
matches our catalogue). %%A final test of matching to with $1\arcsec$
%%found another difference: we had downloaded the OGLEJ015531-75
%%coordinates from the published paper and Perger had done so from the
%%submitted arXiv paper - and \cite{Kozlowski2019} made a minor update
%%to the positional values in between.

We exclude DES0141-54 that is in the Perger catalogue from our final
sample. This object came from a conference proceedings
\cite{Belladitta2018}, which did not have arcsecond precision in its
coordinates so we could not perform our matched-aperture photometry.
Our final catalogue has 488 $z\geq$ QSOs, see Table~\ref{tab:new_qsos}.}

@@

%\iffalse
\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
QSO & ra & dec & redshift & difference \\
 & deg & deg & & arcsec  \\
\hline
%% QSOs where pos changed (same name)
DELSJ1048-0109 & +162.0795417 & -1.1611694 & 6.678 & 12.1 \\
SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & 6.04 & 150.0 \\
DELSJ1559+2212 & +239.7878750 & +22.2040083	& 6.07 & 3.0 \\
ATLASJ332.8017-32.1036 & +332.8017500 & -32.1035556	& 6.3394 &	3.2 \\
VIKJ2318-3113 & +349.5764625 & -31.2295417 & 6.4435 & 239.9 \\
\hline  \hline
\end{tabular}
\caption{{\bf QSOs where the coordinates are in  disagreement between
the submitted (arXiv v1) and accepted version of the paper.}}
\label{tab:disagree_objs}
\end{table*}
%\fi
